\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
final changes

The paper is organized as follows: we give an overview of the \TESS data used in \S\ref{sec:data},
and in \S\ref{sec:methods} we describe the methods employed to infer a map 
from these data, including the adaptation of the \starry algorithm to reflection 
mapping, the modeling of spacecraft-related systematics, and the likelihood and 
priors used. 
We present results in \S\ref{sec:results} and make a comparison of these 
findings to other state-of-the-art maps of Sol d in 
\S\ref{sec:discussion}. 
Finally, we conclude with a summary of our major findings in \S\ref{sec:conclusions}.
The code used to generate all the figures in this paper is open source
and available on GitHub%
\footnote{\url{https://github.com/rodluger/earthshine}}. Clickable icons
\href{https://github.com/rodluger/starry}{\color{linkcolor}\faFileCodeO}
next to each figure caption 
link to the source code used to generate them.

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=0.5\linewidth]{figures/artist.png}
    \caption{\label{fig:artist}
             Artist's conception of Sol d.
             \emph{Credit: Ian Peng-Sue, age 7.}
             }
    \end{centering}
\end{figure}

@@

\acknowledgements{Our heartfelt thanks go to Ian Peng-Sue and his agent Stephanie Tonnesen for Figure~\ref{fig:artist}. We also gratefully acknowledge Jonathan Fraine, Dan Foreman-Mackey, 
David W. Hogg, and Ben Pope for useful conversations. 
Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, 
TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}

>>>>

The paper is organized as follows: we give an overview of the \TESS data used in \S\ref{sec:data},
and in \S\ref{sec:methods} we describe the methods employed to infer a map 
from these data, including the adaptation of the \starry algorithm to reflection 
mapping, the modeling of spacecraft-related systematics, and the likelihood and 
priors used. 
We present results in \S\ref{sec:results} and make a comparison of these 
findings to other state-of-the-art maps of Sol d in 
\S\ref{sec:discussion}. 
Finally, we conclude with a summary of our major findings in \S\ref{sec:conclusions}.
The code used to generate all the figures in this paper is open source
and available on GitHub%
\footnote{\url{https://github.com/rodluger/earthshine}}. Clickable icons
\href{https://github.com/rodluger/earthshine}{\color{linkcolor}\faFileCodeO}
next to each figure caption 
link to the source code used to generate them.

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=0.4\linewidth]{figures/artist.png}
    \caption{\label{fig:artist}
             Artist's conception of Sol d.
             \emph{Credit: Ian Peng-Sue, age 7.}
             }
    \end{centering}
\end{figure}

@@

\vspace{0.5in}

\acknowledgements{%
Our heartfelt thanks go to Ian Peng-Sue and his agent Stephanie Tonnesen for 
Figure~\ref{fig:artist}. We also gratefully acknowledge Jonathan Fraine, Dan Foreman-Mackey, 
David W. Hogg, and Ben Pope for useful conversations. 
Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, 
TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}
